%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Candidate: Seth Nenninger
% ATS-Optimized Version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{article}

% ----- PACKAGES -----
\usepackage[empty]{fullpage}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage[T1]{fontenc} % Ensures better font encoding for character extraction

% Ensure that the generated PDF is machine-readable/ATS-parsable
\input{glyphtounicode}
\pdfgentounicode=1

% ----- DOCUMENT GEOMETRY (ULTRA-TIGHT MARGINS) -----
\geometry{
    left=0.6in,
    right=0.6in,
    top=0.3in, 
    bottom=0.3in
}

% ----- HYPERLINK SETUP -----
\hypersetup{
    colorlinks=true,
    urlcolor=black, % ATS parsers prefer black text
    linkcolor=black,
    pdfborder={0 0 0}
}
\urlstyle{same}

% ----- SECTION FORMATTING -----
\titleformat{\section}{
    \vspace{4pt}\scshape\raggedright\large\bfseries 
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]
\titlespacing{\section}{0pt}{4pt}{4pt}

% ----- CUSTOM COMMANDS -----
% Simple text-based layout (no tables or complex grids) for ATS parsing
\newcommand{\resumeEntry}[4]{
    \vspace{2pt}
    \noindent\textbf{#1}\hfill{#2}
    \newline
    \noindent\textit{#3}\hfill\textit{#4}
    \vspace{-3pt}
}

% Standard round bullet points mapped to standard characters
\newcommand{\resumeItemListStart}{\begin{itemize}[label=$\bullet$, leftmargin=1.1em, itemsep=0pt, parsep=0pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% ----- DOCUMENT START -----
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge Seth Nenninger}
    \vspace{5pt}
    
    Fort Myers, FL \quad | \quad \href{mailto:sethnenninger@gmail.com}{sethnenninger@gmail.com} \quad | \quad \href{https://www.linkedin.com/in/seth-nenninger-bb3897178/}{LinkedIn} \quad |  \quad \href{https://github.com/salmon302}{GitHub}
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}
\vspace{1pt}
\noindent Software Engineer with a proven track record of developing high-performance applications, real-time simulation engines, and automated data pipelines. Adept at leveraging C++ and Python to build scalable solutions, with hands-on experience ensuring 100\% data integrity and strict quality assurance in highly regulated environments. Passionate about applying rigorous engineering principles to solve complex problems across enterprise systems, healthcare technology, and software infrastructure.

%---------- SKILLS ----------
\section{Skills}
\vspace{3pt}
\noindent\textbf{Core Languages:} C++, Python, C\#, JavaScript, Structured Query Language (SQL), AVR Assembly
\vspace{5pt}

\noindent\textbf{Frameworks \& Libraries:} React, FastAPI, Qt, Pandas, PyTorch, OpenGL, JUCE
\vspace{5pt}

\noindent\textbf{Infrastructure \& Tools:} Amazon Web Services (AWS) Elastic Compute Cloud (EC2), Docker, Ansible, Git, Linux, Jira
\vspace{5pt}

\noindent\textbf{Domain Expertise:} Real-Time Engines, Quality Assurance (QA) Protocols, Regulatory Compliance (FDA/cGMP), Data Integrity
\vspace{5pt}

%---------- EDUCATION ----------
\section{Education}
    \resumeEntry
        {Master of Science (MS) in Simulation \& Modeling}
        {August 2026 – May 2028 (Expected)}
        {University of Central Florida}
        {Orlando, FL}
        
    \resumeEntry
        {Bachelor of Science (BS) in Software Engineering}
        {August 2021 – May 2026}
        {Florida Gulf Coast University}
        {Fort Myers, FL}
        
    \resumeEntry
        {Coursework towards Bachelor of Science (BS) in Biochemistry}
        {August 2020 – May 2021}
        {Rochester Institute of Technology}
        {Rochester, NY}

%---------- WORK EXPERIENCE ----------
\section{Work Experience}
    \resumeEntry
        {Backend Engineer Intern}
        {August 2025 - Present}
        {Exonicus}
        {Fort Myers, FL}
    \resumeItemListStart
        \item Architected a Local Area Network (LAN)-based remote control system and dynamic shader parameter foundation for a real-time layered visualization tool, successfully showcased at International Meeting for Simulation in Healthcare (IMSH) 2026 in partnership with Kitware.
        \item Engineered the backend integration between a high-fidelity data engine and Unity, optimizing processing logic and state synchronization to guarantee a consistent 60 Frames Per Second (FPS) performance.
        \item Developed robust validation protocols and comprehensive technical documentation, successfully streamlining the handoff of core infrastructure modules to cross-functional teams and reducing onboarding time.
    \resumeItemListEnd

    \resumeEntry
        {Biologics Processor \& Quality Assurance (QA) Associate}
        {March 2025 – Present}
        {Grifols}
        {Fort Myers, FL}
    \resumeItemListStart
        \item Operate within a highly regulated environment, strictly adhering to Standard Operating Procedures (SOPs) and Current Good Manufacturing Practices (cGMP).
        \item Process over 1,750 biological samples weekly with 99.8\% accuracy, maintaining zero compliance-related rejections during stringent quality assurance audits.
        \item Maintain data integrity for over 3,000 sensitive records, ensuring full traceability, secure data handling, and compliance with federal regulatory standards.
    \resumeItemListEnd

    \resumeEntry
        {Research Assistant – Natural Language Processing (NLP) \& Data Analysis}
        {October 2025 - December 2025}
        {Florida Gulf Coast University}
        {Fort Myers, FL}
    \resumeItemListStart
        \item Utilized Python (Pandas, SciPy, Scikit-learn) to process and analyze large datasets, successfully identifying linguistic markers for predictive modeling.
        \item Built automated data pipelines to perform cross-dataset comparisons, achieving a high statistical correlation of 0.81 in context similarity analysis.
    \resumeItemListEnd
    
    \resumeEntry
        {Student Life Safety Assistant}
        {January 2022 – May 2023}
        {Florida Gulf Coast University}
        {Fort Myers, FL}
    \resumeItemListStart
        \item Conducted rigorous inspections of critical infrastructure, ensuring university-wide compliance with safety codes and operational standards for over 5,000 campus residents.
    \resumeItemListEnd

%---------- PROJECTS ----------
\section{Projects}
    \resumeEntry
        {SMARTArm: Voice \& Vision Controlled Robotic Teleoperation Framework}
        {March 2026 – April 2026}
        {Python, OpenCV, MediaPipe, Flask, C/C++, ESP32, TensorFlow Lite Micro (TFLM)}
        {GitHub: \href{https://github.com/salmon302/SMARTArm/tree/Jacks-Branch}{salmon302/SMARTArm}}
    \resumeItemListStart
        \item Architected a multi-modal teleoperation framework for a 6 Degrees of Freedom (DOF) robotic arm utilizing a "Software-First" approach, achieving real-time spatial control via a single standard webcam without depth sensors.
        \item Engineered real-time kinematic mapping using Google MediaPipe 3D world landmarks, applying dot and cross-product vector mathematics to calculate precise finger flexion and palm orientation.
        \item Resolved joint occlusion and Machine Learning (ML) tracking jitter by integrating the MANO parametric hand model for biomechanical constraints and implementing an adaptive, first-order One Euro low-pass filter.
        \item Designed a high-performance embedded communication bridge using an ESP32-S3 Microcontroller Unit (MCU), replacing JSON with MessagePack binary serialization to compress data payloads by up to 70\% and achieve sub-10ms command latency.
        \item Deployed an Edge Artificial Intelligence (AI) fail-safe by shrinking a neural network by 75\% via 8-bit integer quantization, running a TensorFlow Lite Micro (TFLM) model natively on the MCU for offline emergency processing.
    \resumeItemListEnd

    \resumeEntry
        {JobPipe}
        {April 2026 – May 2026}
        {Python, JavaScript, SQLite, Local NLP Embeddings, Manifest V3, Pytest, LaTeX}
        {GitHub: \href{https://github.com/salmon302/JobPipe}{salmon302/JobPipe}}
    \resumeItemListStart
        \item Engineered a privacy-focused job search automation platform leveraging a Python backend and a custom JavaScript/Manifest V3 browser extension to scrape, ingest, and manage job listings.
        \item Developed a 4-phase algorithmic matching engine using local NLP embeddings (e.g., all-MiniLM) and dynamic keyword weighting to accurately score job relevance against parsed Markdown/LaTeX CV data.
        \item Automated targeted application workflows by building a programmatic pipeline that dynamically injects parsed profile data into LaTeX templates to generate job-specific resume variants.
        \item Designed a robust local storage architecture utilizing SQLite with Full-Text Search (FTS) and versioned schema migrations, integrated with a custom Python native GUI and CLI for seamless user control.
        \item Established strict software reliability standards by architecting a comprehensive test suite with 20+ modules (unit, integration, and E2E) via Pytest, and managing robust package distribution using pyproject.toml.
    \resumeItemListEnd

    \resumeEntry
        {Ad-Velocity: High-Throughput Click Ingestor}
        {February 2026 – April 2026}
        {C\#, .NET Web Application Programming Interface (API), Redis, AWS DynamoDB}
        {GitHub: \href{https://github.com/salmon302/Ad-Velocity}{salmon302/Ad-Velocity}}
    \resumeItemListStart
        \item Architected a scalable, high-throughput ingestion pipeline using a Write-Behind caching pattern for reliable data processing of real-time click events.
        \item Engineered the system to maintain sub-millisecond API latency while successfully buffering traffic spikes of up to 10x normal volume.
        \item Built a Python Graphical User Interface (GUI) load testing tool to simulate high-volume traffic and validate system performance under stress.
    \resumeItemListEnd

    \resumeEntry
        {JUCE VST3 Audio Development Framework}
        {February 2026 – May 2026}
        {C++, JUCE, Python, CMake, PowerShell, VST3 SDK, pluginval}
        {GitHub: \href{https://github.com/salmon302/AgentVST}{salmon302/AgentVST}}
    \resumeItemListStart
        \item Engineered an AI-assisted development framework for cross-DAW audio plugins, leveraging C++ and the JUCE framework to ensure low-latency, real-time Digital Signal Processing (DSP).
        \item Built a custom Python-based scaffolding pipeline to rapidly prototype new plugins, automatically generating C++ DSP logic, testing suites, and documentation for complex audio algorithms.
        \item Automated end-to-end build and deployment workflows by developing native PowerShell and CMake scripts to handle cross-platform compilation and dynamic directory routing.
        \item Implemented strict compliance and regression testing utilizing CTest and pluginval to validate memory safety and ensure universal VST3 standard compatibility across major DAWs (Ableton, Logic Pro).
        \item Developed a production-ready library of 10+ example plugins (including parametric EQs, dynamic compressors, and spatial audio effects) backed by rigorous System Requirements Specifications (SRS) and API documentation.
    \resumeItemListEnd

    \resumeEntry
        {LocalLedger (PDF Data Extraction App) | }
        {December 2025 – February 2026}
        {Python, PyQt6, Pandas, SQLite, pdfplumber, Tesseract OCR, PyInstaller}
        {}
    \resumeItemListStart
        \item Engineered a local-first desktop application in Python designed to automate the extraction and formatting of structured tabular data from unstructured PDF documents.
        \item Developed an interactive, high-performance GUI using PyQt6, featuring a split-screen interface with draggable bounding boxes for visual zone definition and a real-time editable data grid.
        \item Architected a multi-engine parsing pipeline integrating layout-based extraction (pdfplumber), table detection (camelot), and fallback OCR (Tesseract) to ensure high-accuracy data retrieval.
        \item Implemented an automated data transformation layer utilizing Pandas to clean, format (dates/currency), and export data to Excel/CSV, while persisting custom visual extraction templates locally via SQLite.
        \item Streamlined cross-platform deployment by utilizing PyInstaller to compile the application into zero-dependency, standalone executables for Windows and macOS, ensuring a "no-installation" user experience.
    \resumeItemListEnd

    \resumeEntry
        {Emotion-Engine (Real-Time AI Simulation Framework)}
        {July 2025 – December 2025}
        {C++, CMake, Catch2, JSON, Behavior Trees, PowerShell}
        {GitHub: \href{https://github.com/salmon302/JobPipe}{salmon302/JobPipe}}
    \resumeItemListStart
        \item Engineered a high-performance, real-time AI simulation framework in C++, integrating emotion-driven state tracking with a behavior tree decision logic system for autonomous agents.
        \item Architected a dynamic configuration system using the nlohmann/json library to parse external agent behaviors, featuring a hot-reloading capability that allows runtime logic updates without restarting the simulation.
        \item Developed a modular engine architecture utilizing the Blackboard pattern for cross-node state sharing, alongside integrated debugging UI tools (behavior tree visualizer, emotion state overlay) and world boundary management.
        \item Streamlined cross-platform development workflows by configuring CMake (with presets) and writing custom PowerShell/Batch scripts to automate incremental builds and watch modes.
        \item Ensured system reliability and performance by implementing a comprehensive testing suite (unit, integration, and performance metrics) using Catch2, backed by extensive technical documentation.
    \resumeItemListEnd
    
    \resumeEntry
        {DSATrain: AI-Powered Technical Interview Platform}
        {July 2025 – September 2025}
        {React, TypeScript, Python, SQLite, Alembic, REST APIs, Pytest}
        {GitHub: \href{https://github.com/salmon302/DSATrain}{salmon302/DSATrain}}
    \resumeItemListStart
        \item Engineered a full-stack web application using a React/TypeScript frontend and a Python backend to deliver structured algorithmic practice and track user skill progression.
        \item Built robust data ingestion pipelines to aggregate educational content, integrating external REST APIs (Codeforces) via custom Python scripts to dynamically backfill and format problem sets and solutions.
        \item Architected a lightweight, local-first data layer utilizing SQLite, employing Alembic for safe, version-controlled schema migrations to iteratively evolve the relational data model.
        \item Developed advanced content processing workflows capable of parsing complex reading materials and generating synthetic/expert-labeled training data to optimize user learning curves.
        \item Maintained system reliability and code quality by implementing comprehensive backend test coverage using Pytest and standardizing dependency management across the dual-stack environment (npm/pip).
    \resumeItemListEnd



    \resumeEntry
        {CanvasPAL}
        {July 2025 – September 2025}
        {JavaScript, Plasmo Framework, Manifest V3, Vite, Chrome APIs, OAuth}
        {DevPost: \href{https://devpost.com/software/canvaspal-skynet}{devpost/canvaspal}}
    \resumeItemListStart
        \item Engineered a cross-browser extension utilizing the Plasmo Framework and Manifest V3 standards to optimize and automate workflows for the Canvas Learning Management System (LMS).
        \item Architected a background synchronization engine leveraging Chrome's Alarms API and service workers to periodically fetch and align external LMS data (assignments, grades) via secure OAuth integrations.
        \item Designed a robust local persistence layer utilizing the Chrome Storage API and IndexedDB to cache REST API responses and manage user settings, minimizing latency and eliminating external server dependencies.
        \item Developed an event-driven notification system and integrated sample AI-powered assistance tools to provide users with real-time alerts and intelligent workflow enhancements.
        \item Streamlined the development lifecycle and production packaging by utilizing Vite to handle optimized bundling, hot module replacement (HMR), and cross-browser compatibility.
    \resumeItemListEnd




    \resumeEntry
        {Textbook Divider: Optical Character Recognition (OCR) Automation Tool}
        {May 2024 – Present}
        {C++, Python, Tesseract OCR, Audiveris OMR, PoDoFo, ImGui, CMake, Machine Learning (ML)}
        {GitHub: \href{https://github.com/salmon302/Textbook-Divider}{salmon302/Textbook-Divider}}
    \resumeItemListStart
        \item Built an automated document processing tool using Tesseract Optical Character Recognition (OCR), achieving a 99.2\% text extraction accuracy rate.
        \item Optimized image processing algorithms to reduce processing time to 6.7 seconds per page, yielding a 4x efficiency gain in document ingestion.
        \item Engineered a high-performance, hybrid C++/Python application to automate the extraction and structural parsing of complex academic PDFs into navigable components.
        \item Integrated Tesseract OCR and Audiveris OMR engines within the C++ core to accurately ingest and separate standard body text from domain-specific diagrammatic data (musical notation).
        \item Architected a modular Python data pipeline utilizing custom graph extraction algorithms to dynamically identify, process, and analyze embedded relational diagrams and structural patterns.
        \item Implemented efficient document processing capabilities using the PoDoFo library for low-level PDF manipulation, controlled via a custom, lightweight ImGui graphical interface.
        \item Streamlined cross-platform build workflows utilizing CMake and ensured robust system reliability by building a dual-language testing suite encompassing both C++ test runners and Pytest.
    \resumeItemListEnd

    \resumeEntry
        {PYXEngine: Real-Time Audio/DSP Platform}
        {July 2025 – September 2025}
        {Python, SuperCollider, PowerShell, Pytest, DSP, Markdown}
        {Personal Project}
    \resumeItemListStart
        \item Engineered a low-latency audio synthesis engine integrating a Python-based automation framework with SuperCollider to handle real-time Digital Signal Processing (DSP) for therapeutic applications.
        \item Developed specialized algorithmic protocols (e.g., spatial audio, isochronic tones) by combining programmatic audio synthesis with strict validation tooling to ensure compliance with psychoacoustic research standards.
        \item Built a comprehensive user-facing workflow featuring a custom GUI, preset management system, and an Ableton-inspired timeline to abstract and streamline the configuration of complex audio sessions.
        \item Optimized real-time rendering performance and system reliability by implementing safety limiters, DSP enhancements, and robust state management for uninterrupted audio delivery.
        \item Automated continuous integration and local environment setups utilizing PowerShell and Pytest, while maintaining a strict, version-controlled documentation architecture (inventor’s paper trail) for IP tracking and technical specifications.
        
    \resumeItemListEnd
    \resumeEntry
        {Cloud Infrastructure Security Automation}
        {August 2024 – December 2024}
        {Ansible, Amazon Web Services (AWS), Linux} {}
     \resumeItemListStart
        \item Deployed secure AWS EC2 infrastructure using Ansible playbooks for automated provisioning and security hardening.
        \item Mitigated simulated cybersecurity attacks, including Structured Query Language (SQL) injection and Distributed Denial of Service (DDoS), through robust system configuration and monitoring.
     \resumeItemListEnd
    
    \resumeEntry
        {PumpSim: Medical Infusion Pump Simulation}
        {January 2024 – May 2024}
        {AVR Assembly, Embedded Systems} {}
    \resumeItemListStart
        \item Developed a functional simulation of a medical infusion pump using AVR Assembly on an Arduino Microcontroller Unit (MCU).
        \item Programmed precise timing interrupts and user interface logic to simulate critical drug delivery mechanisms safely and accurately.
    \resumeItemListEnd

%---------- AWARDS ----------
\section{Awards}
    \resumeEntry
        {Best Virtual Reality (VR) Game (Medical Training)}
        {December 2025}
        {I/ITSEC Serious Games Showcase \& Challenge}
        {Orlando, FL}
    \resumeItemListStart
        \item Awarded for "MilExTS," a Virtual Reality (VR) Tactical Combat Casualty Care Trainer, recognizing excellence in simulation-based medical education.
    \resumeItemListEnd
    
    \resumeEntry
        {Hertz Company Challenge Winner}
        {February 2025}
        {EagleHacks Hackathon}
        {Fort Myers, FL}
    \resumeItemListStart
        \item Won 1st Place for the best utilization of proprietary datasets to create a scalable software solution.
    \resumeItemListEnd

\end{document}